{RILS}-{ROLS} : Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-12-03 paper_resources/doc/bmc_jbd/bmc_jbd.tex
Small sentence regarding our model accuracy calculation.

\emph{Important note. Exact model accuracy of \textsc{RILS-ROLS} is calculated by dividing the number of successful runs with 1300, i.e., the maximal possible number of successful runs. 
On the other hand, the exact model accuracy of methods revised in \texttt{SRBench} was calculated in a different way. First, the accuracy of each of 130 considered instances was calculated by dividing the number of successful runs with the number of runs that finished its execution. This means that, for example, if some instance was run 10 times, giving 4 successful models, but failing to finish 2 runs due to memory exhaustion or some other OS issue, the accuracy would be 50\% (4/8) instead of 40\% (4/10). Further, these individual accuracies were averaged. 
We do not believe this was the right way to calculate the accuracy, because, this allows one to have high-accuracy method with a low number of successful runs. For example, if method A finishes all of its runs, out of which 650 are successful, its total accuracy will be 50\%. On the other hand, one can have a method B that finishes instances execution in only 4 out of 10 runs, giving 2 successful models each time -- its per-instances accuracy will be 50\%, and after averaging across all instances it will be also 50\%. So, methods A and B will have the same overall accuracy, although method A reached 650 correct solutions, while method B reached only 260.}

>>>>

\emph{Important note. Exact model accuracy of \textsc{RILS-ROLS} is calculated by dividing the number of successful runs with 1300, i.e., the maximal possible number of successful runs. 
On the other hand, the exact model accuracy of methods revised in \texttt{SRBench} was calculated in a different way. First, the accuracy of each of 130 considered instances was calculated by dividing the number of successful runs with the number of runs that finished its execution. This means that, for example, if some instance was run 10 times, giving 4 successful models, but failing to finish 2 runs due to memory exhaustion or some other OS issue, the accuracy would be 50\% (4/8) instead of 40\% (4/10). Further, these individual accuracies were averaged. 
We do not believe this was the right way to calculate the accuracy, because, this allows one to have high-accuracy method with a low number of successful runs. For example, if method A finishes all of its runs, out of which 650 are successful, its total accuracy will be 50\%. On the other hand, one can have a method B that finishes instances execution in only 4 out of 10 runs, giving 2 successful models each time -- its per-instances accuracy will be 50\%, and after averaging across all instances it will be also 50\%. So, methods A and B will have the same overall accuracy, although method A reached 650 correct solutions, while method B reached only 260. Also, note that our calculation cannot overestimate \textsc{RILS-ROLS} exact model accuracy, since denominator is always maximal (1300) -- in essence, non-finished runs are counted as non-successful.}
